The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2016-11-28 manuscript/manuscript.Rnw
add priya's comments and changes
fix space error

%\documentclass[english,12pt]{article}
%\documentclass[5p]{elsarticle_dla}
\documentclass{elsarticle_dla}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\setmathrm{FreeSerif}
\setmathsf{FreeSans}
\setmathtt{FreeSerif}
%\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
%\usepackage[letterpaper]{geometry}
%\usepackage{url}
\usepackage{graphicx}
%\usepackage{rotating}
%\usepackage{wrapfig}
\usepackage{booktabs}
%\usepackage{float}
\usepackage{multirow}
%\usepackage{setspace}
\usepackage[macros=false]{acro}
\usepackage{array}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage[backend=biber,natbib=true,hyperref=true,citestyle=numeric-comp,style=nature,autocite=inline]{biblatex}
\addbibresource{references.bib}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=black,citecolor=blue,breaklinks=true]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads]{endfloat}
% \renewcommand{\efloatseparator}{\mbox{}}
%\AtBeginFigures{\newpage \renewcommand{\efloatseparator}{\mbox{}}\section*{Figure Legends}}
%\AtBeginTables{\newpage \section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
% \renewcommand{\includegraphics}[2][]{}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\newcommand{\DEW}[1]{\textcolor{purple}{\fxnote{DEW: #1}}}
% \usepackage[x11names,svgnames]{xcolor}
% \usepackage{texshade}
% \usepackage{tikz}
\usepackage{nameref}
\usepackage{xspace}
% this package will stretch the font slightly if necessary.
% \usepackage{microtype}
\usepackage{zref-xr,zref-user}
\zxrsetup{toltxlabel}
\zexternaldocument*{supplemental_material}
\usepackage[capitalize]{cleveref}
\def\UrlBreaks{\do\.\do\@\do\\\do\/\do\!\do\_\do\|\do\;\do\>\do\]%
\do\)\do\,\do\?\do\&\do\'\do+\do\=\do\#%
\do\/%
}%
\input{common_latex}
\tolerance=5000
\emergencystretch=0.1pt

@@

@@

@@

The high expression of components of the EGFR signaling pathway in the
core placenta transcriptome (including \textit{GRB2}, \textit{RALB})
as well as annexins which are involved in the location of EGF receptor
localization (\textit{ANXA1} and \textit{ANXA2}) in the core placenta
is consistent with previous findingsshowing that alterations to the
EGF signaling system change invasion of trophoblast cells into the
spiral arteries~\cite{Armant.ea2015:Reducedexpressionofepidermal}.
Another component of the core placenta transcriptome, \textit{CD9},
has been shown to suppress \human extravillous trophoblast
invasion~\cite{Matsumoto.ea2016:CD9suppresseshumanextravillous}, and
we hypothesize that it is responsible for maintaining the balance
between invasion and attachment in the other placentas examined here
as well.

>>>>

%\documentclass[english,12pt]{article}
%\documentclass[5p]{elsarticle_dla}
\documentclass{elsarticle_dla}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\setmathrm{FreeSerif}
\setmathsf{FreeSans}
\setmathtt{FreeSerif}
%\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
%\usepackage[letterpaper]{geometry}
%\usepackage{url}
\usepackage{graphicx}
%\usepackage{rotating}
%\usepackage{wrapfig}
\usepackage{booktabs}
%\usepackage{float}
\usepackage{multirow}
%\usepackage{setspace}
\usepackage[macros=false]{acro}
\usepackage{array}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage[backend=biber,natbib=true,hyperref=true,citestyle=numeric-comp,style=nature,autocite=inline]{biblatex}
\addbibresource{references.bib}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=black,citecolor=blue,breaklinks=true]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads]{endfloat}
% \renewcommand{\efloatseparator}{\mbox{}}
%\AtBeginFigures{\newpage \renewcommand{\efloatseparator}{\mbox{}}\section*{Figure Legends}}
%\AtBeginTables{\newpage \section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
% \renewcommand{\includegraphics}[2][]{}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\newcommand{\DEW}[1]{\textcolor{purple}{\fxnote{DEW: #1}}}
\newcommand{\PP}[1]{\textcolor{orange}{\fxnote{PP: #1}}}
% \usepackage[x11names,svgnames]{xcolor}
% \usepackage{texshade}
% \usepackage{tikz}
\usepackage{nameref}
\usepackage{xspace}
% this package will stretch the font slightly if necessary.
% \usepackage{microtype}
\usepackage{zref-xr,zref-user}
\zxrsetup{toltxlabel}
\zexternaldocument*{supplemental_material}
\usepackage[capitalize]{cleveref}
\def\UrlBreaks{\do\.\do\@\do\\\do\/\do\!\do\_\do\|\do\;\do\>\do\]%
\do\)\do\,\do\?\do\&\do\'\do+\do\=\do\#%
\do\/%
}%
\input{common_latex}
\tolerance=5000
\emergencystretch=0.1pt

@@

\PP{Introduce the characteristics earlier in the introduction}

@@

\PP{Add refs for fusion}

@@

\DEW{Write out FDR for enrichment described}

The high expression of components of the EGFR signaling pathway in the
core placenta transcriptome (including \textit{GRB2}, \textit{RALB})
as well as annexins which are involved in the location of EGF receptor
localization (\textit{ANXA1} and \textit{ANXA2}) in the core placenta
is consistent with previous findings showing that alterations to the
EGF signaling system change invasion of trophoblast cells into the
spiral arteries~\cite{Armant.ea2015:Reducedexpressionofepidermal}.
Another component of the core placenta transcriptome, \textit{CD9},
has been shown to suppress \human extravillous trophoblast
invasion~\cite{Matsumoto.ea2016:CD9suppresseshumanextravillous}, and
we hypothesize that it is responsible for maintaining the balance
between invasion and attachment in the other placentas examined here
as well.

\PP{EGF interacts with S100 from the core placenta as well}
